---
title: "Computational Modeling - Assignment 2"
author: "Stine Fabech Hansson"
date: "29/01/2019"
output: 
  md_document:
    variant: markdown_github
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(rethinking)
library(tidyverse)

```

Making functions

```{r}
# setup
pacman::p_load(pacman, 
               tidyverse, 
               rethinking,
               patchwork) # for ordering plots together

# We make a df for our observations
results_df <- data.frame(teacher = c("RF", "KT", "JS", "MW"),
                         correct = c(3, 2, 160, 66), 
                         n_quest = c(6, 2, 198, 132))

#We define p_grid
p_grid <-   p_grid <- seq(0,1, length.out = 10000)
#We define the bin_size
bin_size <- abs(p_grid[1] - p_grid[2])
#We define an informed prior
inf_prior <- dbeta(p_grid, 8, 4)

#We make a function
calc_teacher <- function(n_correct, n_question, prior, length_out = 10000){
  # this function calculate the posterior
  p_grid <- seq(0,1, length.out = 10000)
  likelihood <- dbinom(n_correct, 
                       size = n_question, 
                       prob = p_grid)
  unstd_posterior <- prior * likelihood
  bin_size <- abs(p_grid[1] - p_grid[2])
  posterior <- unstd_posterior/sum(unstd_posterior * bin_size)
  return(list(teacher_posterior = posterior, 
              likelihood = likelihood,
              grid = p_grid))
}


# We make a function to make a pretty plot
pretty_plot <- function(p_grid, prior, likelihood, posterior, title = " "){
  # define data
  d <- tibble(p_grid = p_grid, 
              prior = prior, 
              likelihood = likelihood,
              posterior = posterior)
  
  # make to long format
  d <- d %>% 
    pivot_longer(cols = c("prior", "likelihood", "posterior"), names_to = "name", values_to = "value")
  
  # make a 
  p <- ggplot(d, aes(x = p_grid, y = value, color = name)) + 
    geom_line() + 
    labs(x = "x", y = "Density", title = title) + 
    theme_bw() + 
    ggplot2::theme(panel.background = element_rect(fill = "white"),
                   panel.border = element_blank()) +
    scale_colour_brewer(palette = "Dark2", direction = 1)
  return(p)
}


```



## In this assignment we learn how to assess rates from a binomial distribution, using the case of assessing your teachers' knowledge of CogSci

N.B. there is a second part at the bottom for next week.

### First part

You want to assess your teachers' knowledge of cognitive science. "These guys are a bunch of drama(turgist) queens, mindless philosophers, chattering communication people and Russian spies. Do they really know CogSci?", you think.

To keep things simple (your teachers should not be faced with too complicated things):
- You created a pool of equally challenging questions on CogSci
- Each question can be answered correctly or not (we don't allow partially correct answers, to make our life simpler).
- Knowledge of CogSci can be measured on a scale from 0 (negative knowledge, all answers wrong) through 0.5 (random chance) to 1 (awesome CogSci superpowers)

This is the data:
- Riccardo: 3 correct answers out of 6 questions
- Kristian: 2 correct answers out of 2 questions (then he gets bored)
- Josh: 160 correct answers out of 198 questions (Josh never gets bored)
- Mikkel: 66 correct answers out of 132 questions

Questions:

1. What's Riccardo's estimated knowledge of CogSci? What is the probability he knows more than chance (0.5) [try figuring this out. if you can't peek into chapters 3.1 and 3.2 and/or the slides]?
- First implement a grid approximation (hint check paragraph 2.4.1!) with a uniform prior, calculate the posterior and plot the results
- Then implement a quadratic approximation (hint check paragraph 2.4.2!).
- N.B. for the rest of the exercise just keep using the grid approximation (we'll move to quadratic approximations in two classes)

```{r}
# Creating uniform prior
prior_uniform <- 1

#Calculating posterior 
rf_uni <- calc_teacher(3, 6, prior_uniform, length_out = 1e4)

# Visualizing posterior 

pretty_plot(rf_uni$grid, prior_uniform, rf_uni$likelihood, rf_uni$teacher_posterior, title = "Probability of Riccardo Being Right")

set.seed(3)

# Creating a tibble from the posterior data 
rf_uni_df <- tibble(p_grid=rf_uni$grid, prior=prior_uniform, likelihood = rf_uni$likelihood, posterior = rf_uni$teacher_posterior)

# Sampling from the posterior 
samples_rf_uni <-
  rf_uni_df %>% 
  sample_n(size = 1e4, weight = posterior, replace = T)

samples_rf_uni %>% 
  ggplot(aes(x = p_grid)) +
  geom_density(fill = "black") +
  coord_cartesian(xlim = 0:1) +
  xlab("Chance of Riccardo being Right (p)")


#Summarizing the posterior 
rf_uni_df %>% 
  filter(p_grid >.5) %>% 
  summarise(sum = sum(posterior))/1e4

# This means the probability of Riccardo performing better than chance is 50 % 

# Quadratic approximation 
globe_qa <-
  rethinking::map(
    alist(
      w ~ dbinom(6, p),  # binomial likelihood
      p ~ dunif(0, 1)    # uniform prior
    ), 
    data = list(w = 3))

# display summary of quadratic approximation
precis(globe_qa)
```

2. Estimate all the teachers' knowledge of CogSci. Who's best? Use grid approximation. Comment on the posteriors of Riccardo and Mikkel.
2a. Produce plots of the prior, and posterior for each teacher.

```{r}
#################### Kristian #########################
#Calculating posterior 
kt_uni <- calc_teacher(2, 2, prior_uniform, length_out = 1e4)

# Visualizing posterior 
pretty_plot(kt_uni$grid, prior_uniform, kt_uni$likelihood, kt_uni$teacher_posterior, title = "Probability of Kristian Being Right")

set.seed(3)

#Creating a tibble from the posterior etc. 
kt_uni_df <- tibble(p_grid=kt_uni$grid, prior=prior_uniform, likelihood = kt_uni$likelihood, posterior = kt_uni$teacher_posterior)

#Sampling from the posterior with sample_n to get a density plot
samples_kt_uni <-
  kt_uni_df %>% 
  sample_n(size = 1e4, weight = posterior, replace = T)

samples_kt_uni %>% 
  ggplot(aes(x = p_grid)) +
  geom_density(fill = "black") +
  coord_cartesian(xlim = 0:1) +
  xlab("Chance of Kristian being Right (p)")

#Sampling from the posterior with sample to get the mean and sd
samples_kt_uni <-
  sample(size = 1e4, x = p_grid, prob = kt_uni_df$posterior, replace = T)

# Getting the mean and sd
mean(samples_kt_uni)
sd(samples_kt_uni)

#Summarizing the posterior 
kt_uni_df %>% 
  filter(p_grid >.5) %>% 
  summarise(sum = sum(posterior))/1e4

#################################### Joshua #################################
#Calculating posterior 
js_uni <- calc_teacher(160, 198, prior_uniform, length_out = 1e4)

# Visualizing posterior 
pretty_plot(js_uni$grid, prior_uniform, js_uni$likelihood, js_uni$teacher_posterior, title = "Proabbility of Joshua Being Right")

set.seed(3)

#Creating a tibble from the posterior etc. 
js_uni_df <- tibble(p_grid=js_uni$grid, prior=prior_uniform, likelihood = js_uni$likelihood, posterior = js_uni$teacher_posterior)

#Sampling from the posterior 
samples_js_uni <-
  js_uni_df %>% 
  sample_n(size = 1e4, weight = posterior, replace = T)

samples_js_uni %>% 
  ggplot(aes(x = p_grid)) +
  geom_density(fill = "black") +
  coord_cartesian(xlim = 0:1) +
  xlab("Chance of Joshua being Right (p)")

#Summarizing the posterior 
js_uni_df %>% 
  filter(p_grid >.5) %>% 
  summarise(sum = sum(posterior))/1e4

#Sampling from the posterior with sample to get the mean and sd
samples_js_uni <-
  sample(size = 1e4, x = p_grid, prob = js_uni_df$posterior, replace = T)

# Getting the mean and sd
mean(samples_js_uni)
sd(samples_js_uni)

################################ Mikkel ####################################
#Calculating posterior 
mw_uni <- calc_teacher(66, 132, prior_uniform, length_out = 1e4)

# Visualizing posterior 
pretty_plot(mw_uni$grid, prior_uniform, mw_uni$likelihood, mw_uni$teacher_posterior, title = "Proabbility of Mikkel Being Right")

set.seed(3)

#Creating a tibble from the posterior etc. 
mw_uni_df <- tibble(p_grid=mw_uni$grid, prior=prior_uniform, likelihood = mw_uni$likelihood, posterior = mw_uni$teacher_posterior)

#Sampling from the posterior 
samples_mw_uni <-
  mw_uni_df %>% 
  sample_n(size = 1e4, weight = posterior, replace = T)

samples_mw_uni %>% 
  ggplot(aes(x = p_grid)) +
  geom_density(fill = "black") +
  coord_cartesian(xlim = 0:1) +
  xlab("Chance of Mikkel being Right (p)")


#Summarizing the posterior 
mw_uni_df %>% 
  filter(p_grid >.5) %>% 
  summarise(sum = sum(posterior))/1e4

#Sampling from the posterior with sample to get the mean and sd
samples_mw_uni <-
  sample(size = 1e4, x = p_grid, prob = mw_uni_df$posterior, replace = T)

# Getting the mean and sd
mean(samples_mw_uni)
sd(samples_mw_uni)

```


3. Change the prior. Given your teachers have all CogSci jobs, you should start with a higher appreciation of their knowledge: the prior is a normal distribution with a mean of 0.8 and a standard deviation of 0.2. Do the results change (and if so how)?
3a. Produce plots of the prior and posterior for each teacher.

```{r}
################################### Riccardo #####################################
# Creating normally distributed prior
p_grid <- seq(from = 0, to = 1, length.out = 1e4)
prior_norm <- dnorm(p_grid, mean = 0.8, sd = 0.20)

#Calculating posterior 
rf_norm <- calc_teacher(3, 6, prior_norm, length_out = 1e4)

# Visualizing posterior 

pretty_plot(rf_norm$grid, prior_norm, rf_norm$likelihood, rf_norm$teacher_posterior, title = "Proabbility of Riccardo Being Right")

set.seed(3)

# Creating a tibble from the posterior data 
rf_norm_df <- tibble(p_grid=rf_norm$grid, prior=prior_norm, likelihood = rf_norm$likelihood, posterior = rf_norm$teacher_posterior)

# Sampling from the posterior 
samples_rf_norm <-
  rf_norm_df %>% 
  sample_n(size = 1e4, weight = posterior, replace = T)

samples_rf_norm %>% 
  ggplot(aes(x = p_grid)) +
  geom_density(fill = "black") +
  coord_cartesian(xlim = 0:1) +
  xlab("Chance of Riccardo being Right (p)")


#Summarizing the posterior 
rf_norm_df %>% 
  filter(p_grid >.5) %>% 
  summarise(sum = sum(posterior))/1e4

#Sampling from the posterior with sample to get the mean and sd
samples_rf_uni <-
  sample(size = 1e4, x = p_grid, prob = rf_uni_df$posterior, replace = T)

# Getting the mean and sd
mean(samples_js_uni)
sd(samples_rf_uni)


################################### Kristian ######################################
#Calculating posterior 
kt_norm <- calc_teacher(2, 2, prior_norm, length_out = 1e4)

# Visualizing posterior 
pretty_plot(kt_norm$grid, prior_norm, kt_norm$likelihood, kt_norm$teacher_posterior, title = "Proabbility of Kristian Being Right")

set.seed(3)

#Creating a tibble from the posterior etc. 
kt_norm_df <- tibble(p_grid=kt_norm$grid, prior=prior_norm, likelihood = kt_norm$likelihood, posterior = kt_norm$teacher_posterior)

#Sampling from the posterior 
samples_kt_norm <-
  kt_norm_df %>% 
  sample_n(size = 1e4, weight = posterior, replace = T)

samples_kt_norm %>% 
  ggplot(aes(x = p_grid)) +
  geom_density(fill = "black") +
  coord_cartesian(xlim = 0:1) +
  xlab("Chance of Kristian being Right (p)")


#Summarizing the posterior 
kt_norm_df %>% 
  filter(p_grid >.5) %>% 
  summarise(sum = sum(posterior))/1e4

#Sampling from the posterior with sample to get the mean and sd
samples_kt_uni <-
  sample(size = 1e4, x = p_grid, prob = kt_uni_df$posterior, replace = T)

# Getting the mean and sd
mean(samples_kt_uni)
sd(samples_kt_uni)

#################################### Joshua #################################
#Calculating posterior 
js_norm <- calc_teacher(160, 198, prior_norm, length_out = 1e4)

# Visualizing posterior 
pretty_plot(js_norm$grid, prior_norm, js_norm$likelihood, js_norm$teacher_posterior, title = "Proabbility of Joshua Being Right")

set.seed(3)

#Creating a tibble from the posterior etc. 
js_norm_df <- tibble(p_grid=js_norm$grid, prior=prior_norm, likelihood = js_norm$likelihood, posterior = js_norm$teacher_posterior)

#Sampling from the posterior 
samples_js_norm <-
  js_norm_df %>% 
  sample_n(size = 1e4, weight = posterior, replace = T)

samples_js_norm %>% 
  ggplot(aes(x = p_grid)) +
  geom_density(fill = "black") +
  coord_cartesian(xlim = 0:1) +
  xlab("Chance of Joshua being Right (p)")


#Summarizing the posterior 
js_norm_df %>% 
  filter(p_grid >.5) %>% 
  summarise(sum = sum(posterior))/1e4

#Sampling from the posterior with sample to get the mean and sd
samples_js_uni <-
  sample(size = 1e4, x = p_grid, prob = js_uni_df$posterior, replace = T)

# Getting the mean and sd
mean(samples_js_uni)
sd(samples_js_uni)

################################ Mikkel ####################################
#Calculating posterior 
mw_norm <- calc_teacher(66, 132, prior_norm, length_out = 1e4)

# Visualizing posterior 
pretty_plot(mw_norm$grid, prior_norm, mw_norm$likelihood, mw_norm$teacher_posterior, title = "Proabbility of Mikkel Being Right")

set.seed(3)

#Creating a tibble from the posterior etc. 
mw_norm_df <- tibble(p_grid=mw_norm$grid, prior=prior_norm, likelihood = mw_norm$likelihood, posterior = mw_norm$teacher_posterior)

#Sampling from the posterior 
samples_mw_norm <-
  mw_norm_df %>% 
  sample_n(size = 1e4, weight = posterior, replace = T)

samples_mw_norm %>% 
  ggplot(aes(x = p_grid)) +
  geom_density(fill = "black") +
  coord_cartesian(xlim = 0:1) +
  xlab("Chance of Mikkel being Right (p)")

#Summarizing the posterior 
mw_norm_df %>% 
  filter(p_grid >.5) %>% 
  summarise(sum = sum(posterior))/1e4

#Sampling from the posterior with sample to get the mean and sd
samples_mw_uni <-
  sample(size = 1e4, x = p_grid, prob = mw_uni_df$posterior, replace = T)

# Getting the mean and sd
mean(samples_mw_uni)
sd(samples_mw_uni)
```


4. You go back to your teachers and collect more data (multiply the previous numbers by 100). Calculate their knowledge with both a uniform prior and a normal prior with a mean of 0.8 and a standard deviation of 0.2. Do you still see a difference between the results? Why?

#### Riccardo ####
```{r}

########## Uniform Prior ################
# Creating uniform prior
prior_uniform <- 1

#Calculating posterior 
rf_uni <- calc_teacher(300, 600, prior_uniform, length_out = 1e4)

# Visualizing posterior 

pretty_plot(rf_uni$grid, prior_uniform, rf_uni$likelihood, rf_uni$teacher_posterior, title = "Proabbility of Riccardo Being Right")

set.seed(3)

# Creating a tibble from the posterior data 
rf_uni_df <- tibble(p_grid=rf_uni$grid, prior=prior_uniform, likelihood = rf_uni$likelihood, posterior = rf_uni$teacher_posterior)

# Sampling from the posterior 
samples_rf_uni <-
  rf_uni_df %>% 
  sample_n(size = 1e4, weight = posterior, replace = T)

samples_rf_uni %>% 
  ggplot(aes(x = p_grid)) +
  geom_density(fill = "black") +
  coord_cartesian(xlim = 0:1) +
  xlab("Chance of Riccardo being Right (p)")

#Summarizing the posterior 
rf_uni_df %>% 
  filter(p_grid >.5) %>% 
  summarise(sum = sum(posterior))/1e4

#Sampling from the posterior with sample to get the mean and sd
samples_rf_uni <-
  sample(size = 1e4, x = p_grid, prob = rf_uni_df$posterior, replace = T)

# Getting the mean and sd
mean(samples_rf_uni)
sd(samples_rf_uni)

##################### Normally distributed prior ################################
# Creating normally distributed prior
p_grid <- seq(from = 0, to = 1, length.out = 1e4)
prior_norm <- dnorm(p_grid, mean = 0.8, sd = 0.20)

#Calculating posterior 
rf_norm <- calc_teacher(300, 600, prior_norm, length_out = 1e4)

# Visualizing posterior 

pretty_plot(rf_norm$grid, prior_norm, rf_norm$likelihood, rf_norm$teacher_posterior, title = "Proabbility of Riccardo Being Right")

set.seed(3)

# Creating a tibble from the posterior data 
rf_norm_df <- tibble(p_grid=rf_norm$grid, prior=prior_norm, likelihood = rf_norm$likelihood, posterior = rf_norm$teacher_posterior)

# Sampling from the posterior 
samples_rf_norm <-
  rf_norm_df %>% 
  sample_n(size = 1e4, weight = posterior, replace = T)

samples_rf_norm %>% 
  ggplot(aes(x = p_grid)) +
  geom_density(fill = "black") +
  coord_cartesian(xlim = 0:1) +
  xlab("Chance of Riccardo being Right (p)")


#Summarizing the posterior 
rf_norm_df %>% 
  filter(p_grid >.5) %>% 
  summarise(sum = sum(posterior))/1e4

#Sampling from the posterior with sample to get the mean and sd
samples_js_uni <-
  sample(size = 1e4, x = p_grid, prob = js_uni_df$posterior, replace = T)

# Getting the mean and sd
mean(samples_js_uni)
sd(samples_js_uni)

```

#### Kristian ####
```{r}
############# Uniform ##################
#Calculating posterior 
kt_uni <- calc_teacher(200, 200, prior_uniform, length_out = 1e4)

# Visualizing posterior 
pretty_plot(kt_uni$grid, prior_uniform, kt_uni$likelihood, kt_uni$teacher_posterior, title = "Proabbility of Kristian Being Right")

set.seed(3)

#Creating a tibble from the posterior etc. 
kt_uni_df <- tibble(p_grid=kt_uni$grid, prior=prior_uniform, likelihood = kt_uni$likelihood, posterior = kt_uni$teacher_posterior)

#Sampling from the posterior 
samples_kt_uni <-
  kt_uni_df %>% 
  sample_n(size = 1e4, weight = posterior, replace = T)

samples_kt_uni %>% 
  ggplot(aes(x = p_grid)) +
  geom_density(fill = "black") +
  coord_cartesian(xlim = 0:1) +
  xlab("Chance of Kristian being Right (p)")


#Summarizing the posterior 
kt_uni_df %>% 
  filter(p_grid >.5) %>% 
  summarise(sum = sum(posterior))/1e4

################### Normally distributed prior ######################
#Calculating posterior 
kt_norm <- calc_teacher(200, 200, prior_norm, length_out = 1e4)

# Visualizing posterior 
pretty_plot(kt_norm$grid, prior_norm, kt_norm$likelihood, kt_norm$teacher_posterior, title = "Proabbility of Kristian Being Right")

set.seed(3)

#Creating a tibble from the posterior etc. 
kt_norm_df <- tibble(p_grid=kt_norm$grid, prior=prior_norm, likelihood = kt_norm$likelihood, posterior = kt_norm$teacher_posterior)

#Sampling from the posterior 
samples_kt_norm <-
  kt_norm_df %>% 
  sample_n(size = 1e4, weight = posterior, replace = T)

samples_kt_norm %>% 
  ggplot(aes(x = p_grid)) +
  geom_density(fill = "black") +
  coord_cartesian(xlim = 0:1) +
  xlab("Chance of Kristian being Right (p)")


#Summarizing the posterior 
kt_norm_df %>% 
  filter(p_grid >.5) %>% 
  summarise(sum = sum(posterior))/1e4

#Sampling from the posterior with sample to get the mean and sd
samples_kt_uni <-
  sample(size = 1e4, x = p_grid, prob = kt_uni_df$posterior, replace = T)

# Getting the mean and sd
mean(samples_kt_uni)
sd(samples_kt_uni)
```

#### Joshua ####
```{r}
############################ Uniform Prior #######################################
#Calculating posterior 
js_uni <- calc_teacher(16000, 19800, prior_uniform, length_out = 1e4)

# Visualizing posterior 
pretty_plot(js_uni$grid, prior_uniform, js_uni$likelihood, js_uni$teacher_posterior, title = "Proabbility of Joshua Being Right")

set.seed(3)

#Creating a tibble from the posterior etc. 
js_uni_df <- tibble(p_grid=js_uni$grid, prior=prior_uniform, likelihood = js_uni$likelihood, posterior = js_uni$teacher_posterior)

#Sampling from the posterior 
samples_js_uni <-
  js_uni_df %>% 
  sample_n(size = 1e4, weight = posterior, replace = T)

samples_js_uni %>% 
  ggplot(aes(x = p_grid)) +
  geom_density(fill = "black") +
  coord_cartesian(xlim = 0:1) +
  xlab("Chance of Joshua being Right (p)")


#Summarizing the posterior 
js_uni_df %>% 
  filter(p_grid >.5) %>% 
  summarise(sum = sum(posterior))/1e4

#Sampling from the posterior with sample to get the mean and sd
samples_js_uni <-
  sample(size = 1e4, x = p_grid, prob = js_uni_df$posterior, replace = T)

# Getting the mean and sd
mean(samples_js_uni)
sd(samples_js_uni)


############################ Normally Distributed #################################
#Calculating posterior 
js_norm <- calc_teacher(16000, 19800, prior_norm, length_out = 1e4)

# Visualizing posterior 
pretty_plot(js_norm$grid, prior_norm, js_norm$likelihood, js_norm$teacher_posterior, title = "Probability of Joshua Being Right")

set.seed(3)

#Creating a tibble from the posterior etc. 
js_norm_df <- tibble(p_grid=js_norm$grid, prior=prior_norm, likelihood = js_norm$likelihood, posterior = js_norm$teacher_posterior)

#Sampling from the posterior 
samples_js_norm <-
  js_norm_df %>% 
  sample_n(size = 1e4, weight = posterior, replace = T)

samples_js_norm %>% 
  ggplot(aes(x = p_grid)) +
  geom_density(fill = "black") +
  coord_cartesian(xlim = 0:1) +
  xlab("Chance of Joshua being Right (p)")


#Summarizing the posterior 
js_norm_df %>% 
  filter(p_grid >.5) %>% 
  summarise(sum = sum(posterior))/1e4

#Sampling from the posterior with sample to get the mean and sd
samples_js_uni <-
  sample(size = 1e4, x = p_grid, prob = js_uni_df$posterior, replace = T)

# Getting the mean and sd
mean(samples_js_uni)
sd(samples_js_uni)
```

#### Mikkel ####
```{r}
############################### Uniform Prior ####################################
#Calculating posterior 
mw_uni <- calc_teacher(6600, 13200, prior_uniform, length_out = 1e4)

# Visualizing posterior 
pretty_plot(mw_uni$grid, prior_uniform, mw_uni$likelihood, mw_uni$teacher_posterior, title = "Proabbility of Mikkel Being Right")

set.seed(3)

#Creating a tibble from the posterior etc. 
mw_uni_df <- tibble(p_grid=mw_uni$grid, prior=prior_uniform, likelihood = mw_uni$likelihood, posterior = mw_uni$teacher_posterior)

#Sampling from the posterior 
samples_mw_uni <-
  mw_uni_df %>% 
  sample_n(size = 1e4, weight = posterior, replace = T)

samples_mw_uni %>% 
  ggplot(aes(x = p_grid)) +
  geom_density(fill = "black") +
  coord_cartesian(xlim = 0:1) +
  xlab("Chance of Mikkel being Right (p)")


#Summarizing the posterior 
mw_uni_df %>% 
  filter(p_grid >.5) %>% 
  summarise(sum = sum(posterior))/1e4

#Sampling from the posterior with sample to get the mean and sd
samples_mw_uni <-
  sample(size = 1e4, x = p_grid, prob = mw_uni_df$posterior, replace = T)

# Getting the mean and sd
mean(samples_mw_uni)
sd(samples_mw_uni)

############################### Normally Distributed ############################
#Calculating posterior 
mw_norm <- calc_teacher(6600, 13200, prior_norm, length_out = 1e4)

# Visualizing posterior 
pretty_plot(mw_norm$grid, prior_norm, mw_norm$likelihood, mw_norm$teacher_posterior, title = "Proabbility of Mikkel Being Right")

set.seed(3)

#Creating a tibble from the posterior etc. 
mw_norm_df <- tibble(p_grid=mw_norm$grid, prior=prior_norm, likelihood = mw_norm$likelihood, posterior = mw_norm$teacher_posterior)

#Sampling from the posterior 
samples_mw_norm <-
  mw_norm_df %>% 
  sample_n(size = 1e4, weight = posterior, replace = T)

samples_mw_norm %>% 
  ggplot(aes(x = p_grid)) +
  geom_density(fill = "black") +
  coord_cartesian(xlim = 0:1) +
  xlab("Chance of Mikkel being Right (p)")

#Summarizing the posterior 
mw_norm_df %>% 
  filter(p_grid >.5) %>% 
  summarise(sum = sum(posterior))/1e4

#Sampling from the posterior with sample to get the mean and sd
samples_mw_uni <-
  sample(size = 1e4, x = p_grid, prob = mw_uni_df$posterior, replace = T)

# Getting the mean and sd
mean(samples_mw_uni)
sd(samples_mw_uni)
```

5. Imagine you're a skeptic and think your teachers do not know anything about CogSci, given the content of their classes. How would you operationalize that belief?

6. Optional question: Can you estimate the difference between Riccardo's estimated knowledge and that of each of the other teachers? Would you deem it credible (that is, would you believe that it is actually different)?


### Second part: Focusing on predictions

Last year you assessed the teachers (darned time runs quick!). Now you want to re-test them and assess whether your models are producing reliable predictions. In Methods 3 we learned how to do machine-learning style assessment of predictions (e.g. rmse on testing datasets). Bayesian stats makes things a bit more complicated. So we'll try out how that works. N.B. You can choose which prior to use for the analysis of last year's data.

Questions to be answered (but see guidance below):
1- Write a paragraph discussing how assessment of prediction performance is different in Bayesian vs. frequentist models
2- Provide at least one plot and one written line discussing prediction errors for each of the teachers.

This is the old data:
- Riccardo: 3 correct answers out of 6 questions
- Kristian: 2 correct answers out of 2 questions (then he gets bored)
- Josh: 160 correct answers out of 198 questions (Josh never gets bored)
- Mikkel: 66 correct answers out of 132 questions

This is the new data:
- Riccardo: 9 correct answers out of 10 questions (then he freaks out about teaching preparation and leaves)
- Kristian: 8 correct answers out of 12 questions
- Josh: 148 correct answers out of 172 questions (again, Josh never gets bored)
- Mikkel: 34 correct answers out of 65 questions

Guidance Tips

1. There are at least two ways of assessing predictions.
2. Last year's results are this year's expectations.
3. Are the parameter estimates changing? (way 1)
4. How does the new data look in last year's predictive posterior? (way 2)

```{r}
#creating a dataframe of the results
results_df = data.frame(teacher = c("RF", "KT", "JS", "MW"), 
                        correct = c(3, 2, 160, 66) , 
                        n_quest = c(6, 2, 198, 132))

results_df_2 <- data.frame(teacher = c("RF", "KT", "JS", "MW"),
                           correct = c(9, 8, 148, 34),
                           n_quest = c(10, 12, 172, 65))

#Grid approximation 
length = 1e4 #10.000
p_grid <- seq(0, 1, length.out = length)
inf_prior <- dnorm(p_grid, mean = 0.8, sd = 0.20)

rf_results <- calc_teacher(2, 2, prior = inf_prior)

### Kristian ###
#Old posterior 
kt_results <- calc_teacher(2, 2, prior = inf_prior)

#New posterior
kt_results_2 <- calc_teacher(8, 12, prior = kt_results$teacher_posterior)

pretty_plot(p_grid = kt_results_2$grid, 
            prior = kt_results$teacher_posterior, 
            likelihood = kt_results_2$likelihood, 
            posterior = kt_results_2$teacher_posterior, title = "New Posterior Distribution Kristian")


js_results <- calc_teacher(2, 2, prior = inf_prior)


mw_results <- calc_teacher(2, 2, prior = inf_prior)

```

